{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-27 documents/application.tex
Optimal control

Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^{-4}$ V/m $\times$ Hz (\cite{RSS1022015}, Table 4) - that is, $0.81 \times 10^6$ V/m @ 6 GHz to $1.2 \times 10^6$ V/m @ 9 GHz. It should be noted that more recent standards have abandoned instantaneous electric field limits, finding that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).\footnotemark

@@

Considering only the electric field skin depth\footnotemark\cite{Safety2001}\cite{Physical1982} of average lung tissue\cite{gabriel1996compilation}\cite{Dielectricb}\cite{Dielectric}\cite{Tissue2018} (which changes considerably based on inflation), at 8 GHz it appears to be possible to achieve the required field of 150 V/m at a very reasonable depth of 60 mm. We could not find any data on the distribution of gas exchange throughout the cross-section of the lung.

>>>>

Industry Canada limits on the instantaneous electric field anywhere inside the body are $1.35 \times 10^{-4}$ V/m $\times$ Hz (\cite{RSS1022015}, Table 4) - that is, $0.81 \times 10^6$ V/m @ 6 GHz to $1.2 \times 10^6$ V/m @ 9 GHz. It should be noted that more recent standards have abandoned instantaneous electric field limits altogether, asserting that they have little biological rationale (\cite{C95}, B.4.3, {\it Rationale for pulsed RF field limits}).\footnotemark

In addition to these limits, the "microwave hearing threshold" - the pulse energy density threshold at which nerve stimulation begins to occur, should be respected.

@@

Considering only the electric field skin depth\footnotemark\cite{Safety2001}\cite{Physical1982} of average lung tissue\cite{gabriel1996compilation}\cite{Dielectricb}\cite{Dielectric}\cite{Tissue2018} (which changes considerably based on inflation), at 8 GHz it appears to be possible to achieve the required field of 150 V/m at a very reasonable depth of 60 mm.

We could not find any data on the distribution of gas exchange throughout the cross-section of the lung.

### 2020-11-27 documents/detection.tex
Optimal control

>>>>

Biotium Gelgreen has a very specific advantage: to increase the safety of the dye, the flurophore is tied to some huge proprietary molecule, preventing it from diffusing through membranes or capsids. This has the side effect of making the fluorescence intensity strictly related to the quantity of genomic material dispersed in the solvent, rather than
